NFC and burnout in teachers - A replication and extension study

### 2021-09-08 Manuscript/Manuscript.Rmd
changed recoding to correct version for Work Satisfaction Scale

  mbi <- data[,10:30]             # Maslach Burnout Inventory
  erq <- data[,31:40]             # Emotion Regulation Questionnaire
  scs <- data[,41:53]             # Self Control Scale
  ws <- data[,54:90]              # Work Satisfaction
  ncs <- data[,c(91:98,100:107)]  # Need for Cognition Scale (without the dummy item)
  covb <- data[,108:118]          # Covid Burden Items
  dth <- ws[,c(4,8,9)]            # the Work Satisfaction items for the latent variable Demands Too High
  dtl <- ws[,c(12,26,27)]         # the Work Satisfaction items for the latent variable Demands Too Low
  drf <- ws[,c(17,21,24)]         # the Work Satisfaction items for the latent variable Demand-Resource-Fit

@@

  mbi[,keylist$mbi_rpe] <- 7 - mbi[,keylist$mbi_rpe]  # Recode from 1-6 to 6-1
  scs[,keylist$scs] <- 6 - scs[,keylist$scs]          # Recode from 1-5 to 5-1
  scs <- scs - 3                                      # Recode all from 1-5 to -2-+2
  ncs[,keylist$ncs] <- 8 - ncs[,keylist$ncs]          # Recode from 1-7 to 7-1
  ncs <- ncs - 4                                      # Recode all from 1-7 to -3-+3
  ws[,keylist$ws] <- 6 - ws[,keylist$ws]              # Recode from 1-5 to 5-1
  ws <- ws - 3                                        # Recode all from 1-5 to -2-+2
  covb[,c(2,3,4,9)] <- 4 - covb[,c(2,3,4,9)]          # Recode from 1-3 to 3-1
  covb[,8] <- 3 - covb[,8]                            # Recode from 1-2 to 2-1
  dth <- dth - 3                                      # Recode all from 1-5 to to -2-+2
  dtl <- 6 - dtl                                      # Recode from 1-5 to to 5-1
  dtl <- dtl - 3                                      # Recode all from 1-5 to to -2-+2
  drf <- drf -3                                       # Recode all from 1-5 to to -2-+2

@@

  # total effect
    Total := c + (a1 * b1) + (a2 * b2) + (a3 * b3)

  # Include covariance of mediators in the model
    scs ~~ erq_reap
    scs ~~ erq_supp
    erq_reap ~~ erq_supp'

@@

  # structural model
    DTH ~ NFC
    DTL ~ NFC
    DRF ~ NFC
    MBI ~ NFC + DTH + DTL + DRF'

@@

  fit2_plot <- semPaths(fit2, what = "par",
                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","ee","dp","rpe","NFC","DTH","DTL","DRF","MBI"),
                        layout = matrix(data = c(-1,-0.8,-0.6,-0.4,-0.8,-0.6,-0.4,-0.2,0,0.2,0.4,0.6,0.8,0.6,0.8,1,-0.8,-0.6,0,0.6,0.8,
                                                 -1,-1,-1,-1,1,1,1,1,1,1,1,1,1,-1,-1,-1,-0.5,0.5,0.5,0.5,-0.5),
                                        nrow = 21, ncol = 2),
                        residuals = FALSE, fade = FALSE,
                        edge.label.cex = 1, # size of the parameters
                        edge.label.color = "black", edge.label.bg = FALSE, # color and background of the parameters
                        posCol = "#f0a543", negCol = "#5a99d1" # color of arrows
  )
```

>>>>

  mbi <- data[,10:30]             # Maslach Burnout Inventory grep(‚ncs‘, colnames(data))
  erq <- data[,31:40]             # Emotion Regulation Questionnaire
  scs <- data[,41:53]             # Self Control Scale
  ws <- data[,54:90]              # Work Satisfaction
  ncs <- data[,c(91:98,100:107)]  # Need for Cognition Scale (without the dummy item)
  covb <- data[,108:118]          # Covid Burden Items
  dth <- ws[,c(4,8,9)]            # the Work Satisfaction items for the latent variable Demands Too High
  dtl <- ws[,c(12,26,27)]         # the Work Satisfaction items for the latent variable Demands Too Low
  drf <- ws[,c(17,21,24)]         # the Work Satisfaction items for the latent variable Demand-Resource-Fit

@@

  mbi[,keylist$mbi_rpe] <- 7 - mbi[,keylist$mbi_rpe]  # Recode from 1-6 to 6-1
  scs[,keylist$scs] <- 6 - scs[,keylist$scs]          # Recode from 1-5 to 5-1
  scs <- scs - 3                                      # Recode all from 1-5 to -2-+2
  ncs[,keylist$ncs] <- 8 - ncs[,keylist$ncs]          # Recode from 1-7 to 7-1
  ncs <- ncs - 4                                      # Recode all from 1-7 to -3-+3
  ws[,keylist$ws] <- 6 - ws[,keylist$ws]              # Recode from 1-5 to 5-1
  ws <- ws - 3                                        # Recode all from 1-5 to -2-+2
  covb[,c(2,3,4,9)] <- 4 - covb[,c(2,3,4,9)]          # Recode from 1-3 to 3-1
  covb[,8] <- 3 - covb[,8]                            # Recode from 1-2 to 2-1
  dth <- 6 - dth
  dth <- dth - 3                                      # Recode all from 1-5 to to -2-+2
  dtl <- dtl - 3                                      # Recode all from 1-5 to to -2-+2
  drf <- 6 - drf
  drf <- drf -3                                       # Recode all from 1-5 to to -2-+2

@@

  # total effect
    Total := c + (a1 * b1) + (a2 * b2) + (a3 * b3)
'

@@

  # structural model
    DTH ~ a1 * NFC
    DTL ~ a2 * NFC
    DRF ~ a3 * NFC
    MBI ~ c * NFC + b1 * DTH + b2 * DTL + b3 * DRF

  # total effect
    Total := c + (a1 * b1) + (a2 * b2) + (a3 * b3)'

@@

  fit2_plot <- semPaths(fit2, what = "std",
                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","ee","dp","rpe","NFC","DTH","DTL","DRF","MBI"),
                        layout = matrix(data = c(-1,-0.8,-0.6,-0.4,-0.8,-0.6,-0.4,-0.2,0,0.2,0.4,0.6,0.8,0.6,0.8,1,-0.8,-0.6,0,0.6,0.8,
                                                 -1,-1,-1,-1,1,1,1,1,1,1,1,1,1,-1,-1,-1,-0.5,0.5,0.5,0.5,-0.5),
                                        nrow = 21, ncol = 2),
                        residuals = FALSE, fade = FALSE,
                        edge.label.cex = 1, # size of the parameters
                        edge.label.color = "black", edge.label.bg = FALSE, # color and background of the parameters
                        posCol = "#f0a543", negCol = "#5a99d1" # color of arrows
  )
```
